Ricci-Ollivier Curvature of the Rooted Phylogenetic Subtree-Prune-Regraft Graph\tnoteref{t1,t2}

### 2016-12-02 curvature.tex
Adding my fancygrant.

	\tnotetext[t1]{This work was funded by National Science Foundation award 1223057.}
	\tnotetext[t2]{A preliminary version of this work appeared in the 2016 Proceedings of the Thirteenth Workshop on Analytic Algorithmics and Combinatorics (ANALCO).}

@@

\cortext[cor1]{Corresponding author}
\fntext[fn1]{Chris Whidden is a Simons Foundation Fellow of the Life Sciences Research Foundation.}

>>>>

	\tnotetext[t1]{This work was funded by National Science Foundation award 1223057.
Chris Whidden is a Simons Foundation Fellow of the Life Sciences Research Foundation.
The research of Frederick Matsen was supported in part by a Faculty Scholar grant from the Howard Hughes Medical Institute and the Simons Foundation.
    }
	\tnotetext[t2]{A preliminary version of this work appeared in the 2016 Proceedings of the Thirteenth Workshop on Analytic Algorithmics and Combinatorics (ANALCO).}

@@

\cortext[cor1]{Corresponding author}
